An Open Repository of Real-Time COVID-19 Indicators

### 2021-10-08 forecast/paper/response-to-reviewers.tex

  In principle,
  we would expect that different weights may alter the conclusions, though
  likely not substantively. Applying a monotone function to $\tau$ only effectively
  changes the quantile of interest, resulting in a mismatch between the coverage you
  tried to get and the coverage WIS is evaluating. Applying the function to $\tau$
  and $(1-\tau)$ results in an asymmetry, penalizing forecasts that miss on one
  side more than on the other.

  $\bullet$ We have added a sentence in the Evaluation Metrics section emphasizing that
  this metric is standard.
\end{resp}

  2. They do not discuss the possible effects of vaccination rates and other
  factors, though this may be one of the areas of localization they propose to
  investigate.

\begin{resp}
  During the period discussed in the main paper, vaccinations had essentially no
  effect. On Dec 31 2000, when the main evaluation period ends,  according to
  CDC data, about 1\% of the population 
  had received 1 dose. That said, we should probably be more specific in the
  paragraph on lines 31-40: our goal is to use very simple models that do not
  account for extra information (vaccinations but also strains of the virus,
  ``super-spreader'' events, etc.).

  $\bullet$ We have added a sentence around lines 30--40 emphasizing the choice
  to ignore such factors.
\end{resp}

@@

\begin{resp}
  There is little reason to believe that this data is stationary. The models
  however are trained and evaluated over reasonably short periods (2-3 months),
  over which time the behavior may well be stationary. We have added a section
  to the appendix that uses the cumulative sum normalized by baseline as
  suggested. With some exceptions at the beginning of 
  the evaluation period, the relative ordering remains fairly consistent. The AR
  model is easily the worst.

\end{resp}

2. Are the results in this paper statistically significant? I see no discussion
of this question, which seems unbelievable for me to be saying, given the
authorship. And yet here I am.

\begin{resp}
  As noted in the introduction, there are no options available for fully 
  rigorous and nonparametric (model-free) statistical significance testing,
  giving the intricate spatiotemporal dependence in our forecasting problem.

  We also have strong reasons for not using model-based approaches (in part due
  to nonstationarity, but also due to the belief that these models are not
  applicable here). We felt that our extensive predictive comparisons in the
  methods section and supplement were more appropriate.

  That said, to address this more directly we have made a number of additions:

  $\bullet$ We have added a section to the Supplement (and point
  to it around 
  line 458 in the main text), that performs a Sign Test for differences in
  accuracy. P-values there tend to cluster near zero and one suggesting some
  periods have significantly improved accuracy for the indicator-assisted models
  while in others, the reverse is true.

### 2021-10-08 indicators/paper/paper.tex

\paragraph{Internet-Based Surveys} Conducted in partnership with Facebook,
Delphi's COVID-19 Trends and Impact Survey receives an average of 50,000
responses daily, and has received over 25 million responses since April 2020
\cite{Salomon:2021, Kreuter:2020}. From the surveys, we construct indicators on
symptoms, social distancing, vaccination, and other attitudes and behaviors
related to COVID. The surveys are voluntary and participants are redirected to a
platform managed by Carnegie Mellon University to give consent and take the
survey; individual response data is not provided to Facebook and the data
collection protocol was approved by the Carnegie Mellon Institutional Review
Board (STUDY2020\_00000162).

@@

Figure~\ref{fig:backfill-compare} shows relative differences between early
indicator values, reported 10--90 days after the underlying events, and later
versions at least four months later. As the distribution of these revision
amounts is highly skewed, the figure plots the 95th percentile of relative
change, showing that reported deaths can incur large relative error in initial
values, comparable to that in claims-based signals. However, for deaths, as well
as cases, these large revisions are not very systematic, with large corrections
typically occurring at a sparse subset of locations and times (e.g., due to 
audits or backlogs being cleared, which can result in thousands of cases or
deaths can be added or removed all at once). This backfill is much more
difficult to predict than that of claims data, therefore the latter (and other
sources) may be useful for nowcasting cases and deaths while public health
reports are being aggregated and corrected.

>>>>

\paragraph{Internet-Based Surveys} Conducted in partnership with Facebook,
Delphi's COVID-19 Trends and Impact Survey receives an average of 50,000 responses
daily, and has received over 25 million responses since April 2020
\cite{Salomon:2021, Kreuter:2020}. From the surveys, we construct indicators on
symptoms, social distancing, vaccination, and other attitudes and behaviors
related to COVID.

@@

Figure~\ref{fig:backfill-compare} shows relative differences between early
indicator values, reported 10--90 days after the underlying events, and later
versions at least four months later. As the distribution of these revision
amounts is highly skewed, the figure plots the 95th percentile of relative
change, showing that reported deaths can incur large relative error in initial
values, comparable to that in claims-based signals. However, for deaths, as well
as cases, these large revisions are not very systematic, with large corrections
typically occuring at a sparse subset of locations and times (e.g., due to
audits or backlogs being cleared, which can result in thousands of cases or
deaths can be added or removed all at once). This backfill is much more
difficult to predict than that of claims data, therefore the latter (and other
sources) may be useful for nowcasting cases and deaths while public health
reports are being aggregated and corrected.

### 2021-10-08 indicators/paper/supplement.Rmd

>>>>

\clearpage
```{r case-correlation-lagged-data}
start_day <- "2020-04-15"
end_day <- "2021-04-15"
as_of_day <- "2021-06-01"

df_cases <- covidcast_signal("jhu-csse", "confirmed_7dav_incidence_prop",
                             start_day, end_day, as_of = as_of_day)

names <- c("7 days", "14 days", "21 days")
lags <- c(7, 14, 21)
df_cor <- vector("list", length(lags))

for (ii in seq_along(lags)) {
  df_cor[[ii]] <- covidcast_cor(df_cases, df_cases, dt_y = lags[ii],
                                by = "time_value")
  df_cor[[ii]]$signal <- names[ii]
}

df <- do.call(rbind, df_cor)
df$signal <- factor(df$signal, levels = names, labels = names)
```

```{r case-correlation-lagged-plot, fig.cap="Correlation between confirmed cases and case reports 1, 2, or 3 weeks prior, for all counties in the United States with case reporting. Cases are correlated with future cases as one might expect, but note the precipitous drop in correlation in February 2021. This matches the correlation drop between other COVIDcast signals and cases during the same time period, supporting the hypothesis that the drop was due to decreased heterogeneity in case rates by county."}
ggplot(df, aes(x = time_value, y = value)) +
  geom_line(aes(color = signal)) +
  ylim(0, NA) +
  labs(x = "Date", y = "Correlation") +
  scale_x_date(date_breaks = "3 months", date_labels = "%b %Y",
               date_minor_breaks = "1 month") +
  theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank())
```
